### 2020-04-22 system-model.tex
:pencil: Vectorize phase shift matrix

	\begin{subsection}{Single-User Optimization}
		In this section, we first characterize the rate-energy region in the single-user setup. Let $h_n={A_n}{e^{j{\bar{\psi}_n}}}$, $w_{I,n}=s_{I,n}e^{j{\phi}_n}$, and $w_{P,n}=s_{P,n}e^{j{\phi}_n}$. Consider the rate maximization problem subject to transmit power and output DC current constraints
		\begin{maxi}
			{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta}_0,\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{(h_{D,n}+\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})w_{I,n}}\rvert^2}{\sigma_n^2}\right)}}{\label{op:1}}{}
			\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
			\addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta}_0,\rho)\ge{\bar{z}}}
			\addConstraint{0\le{\theta_l}\le{2{\pi}},\quad l=1,\dots,L}
		\end{maxi}
		Since the objective function is non-convex with $\Theta_0$ and $\boldsymbol{w}_I$ coupled, \ref{op:1} is a non-convex problem. To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that updates the information weight at the transmitter and the phase shifts at the IRS iteratively until convergence. It leads to a local optimum and is sensitive to the initialization of $\Theta_0$, $\boldsymbol{w}_I$ and $\boldsymbol{w}_P$.
		% Moreover, a feasible phase design strategy that maximizes the effective composite channel is used for phase shift initialization.

>>>>

	\begin{subsection}{Single-User Optimization}
		In this section, we first characterize the rate-energy region in the single-user setup. Define $h_n={A_n}{e^{j{\bar{\psi}_n}}}$, $w_{I,n}=s_{I,n}e^{j{\phi}_n}$, $w_{P,n}=s_{P,n}e^{j{\phi}_n}$
		, $\boldsymbol{v}=[e^{j{\theta_1}},\dots,e^{j{\theta_L}}]^H \in \mathbb{C}^{L \times 1}$, and $\boldsymbol{\Phi}_n=\mathrm{diag}\left\{\boldsymbol{h}_{R,n}\right\}\boldsymbol{h}_{I,n} \in \mathbb{C}^{L \times 1}$. On top of this, the composite channel \ref{eq:h_{k,n}} can be expressed as $h_n=h_{D,n}+\boldsymbol{v}^H{\boldsymbol{\Phi}_n}$. The WSR-E region can be obtained through a rate maximization problem subject to transmit power and output DC current constraints
		\begin{maxi}
			% {\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta}_0,\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{(h_{D,n}+\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})w_{I,n}}\rvert^2}{\sigma_n^2}\right)}}{\label{op:1}}{}
			{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{v},\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(h_{D,n}+\boldsymbol{v}^H{\boldsymbol{\Phi}_n})w_{I,n}\rvert^2}{\sigma_n^2}\right)}}{\label{op:1}}{}
			\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
			\addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{v},\rho)\ge{\bar{z}}}
			\addConstraint{\lvert{v_l}\rvert=1,\quad l=1,\dots,L}
			% \addConstraint{0\le{\theta_l}\le{2{\pi}},\quad l=1,\dots,L}
		\end{maxi}
		\ref{op:1} is nontrivial due to the non-convex objective function, unit-modulus constraint, and coupled variables. To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that updates the phase shifts at the IRS and the information weight at the transmitter iteratively until convergence.

		The phase optimization problem can be formed as follows. For a fixed information weight $\boldsymbol{w}_I$ and power-splitting ratio $\rho$, problem \ref{op:1} reduces to
		\begin{maxi}
			{\boldsymbol{\boldsymbol{v}}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(h_{D,n}+\boldsymbol{v}^H{\boldsymbol{\Phi}_n})\rvert^2\lvert{w}_{I,n}\rvert^2}{\sigma_n^2}\right)}}{}{}
		\end{maxi}

		% It leads to a local optimum and is sensitive to the initialization of $\Theta_0$, $\boldsymbol{w}_I$ and $\boldsymbol{w}_P$.
		% Moreover, a feasible phase design strategy that maximizes the effective composite channel is used for phase shift initialization.
